Contextuality and Nonlocality in Discrete Quantum Theory

### 2015-11-30 DQC3.tex
Further remove useless comments on "The Concept of Contextuality and..."

\yutsung{Does the sentences in this paragraph contradict to each
other? According to the postulates in page 207 in Peres~\cite{peres1995quantum},
the last sentence should be ``To be more precise, as noted by Peres~\cite{peres1995quantum}
and Mermin~\cite{MerminPRL1990}, it is impossible to predetermine
definite measurement outcomes for all observables on a system, such
that the predetermined outcome of any observable does not depend on
whether we measure the observable alone, or along with arbitrary sets
of mutually commuting observables.''

Let $v\left(\mathbf{O}\right)$ be the predetermined definite outcome
of an observable $\mathbf{O}$, then we can define $v'$ on states
by their projector $v'\left(\ket{n}\right)=v\left(\proj{n}\right)$.
Because lack of commuting observables in Schumacher and Westmoreland~\cite{2010arXiv1010.5452S},
they use ``$v'$ is well-defined'' as the definition of non-contextuality.

Besides, if the result of measuring an observable depends on simultaneously
measuring commuting observables, then the usual slogan ``two commuting
operators can be simultaneously measured'' is just confusing... }

>>>>

\yutsung{According to the postulates in page 207 in Peres~\cite{peres1995quantum},
the last sentence should be ``To be more precise, as noted by Peres~\cite{peres1995quantum}
and Mermin~\cite{MerminPRL1990}, it is impossible to predetermine
definite measurement outcomes for all observables on a system, such
that the predetermined outcome of any observable does not depend on
whether we measure the observable alone, or along with arbitrary sets
of mutually commuting observables.''}
